### 2023-04-24 manuscript/manus.Rmd
Prepared for manuscript typesetting in R

---
output:
  bookdown::pdf_document2: 
    toc: no
    keep_tex: yes
  #bookdown::word_document2: default
fig_caption: yes
always_allow_html: yes
bibliography: 
  references.bib
#csl: biomed-central.csl #get Zotero running to work
# These are LaTex settings to take care of floating figures/tables, line spacing, etc
header-includes:
  - \usepackage{endfloat}    
  - \usepackage{setspace}\doublespacing
  - \usepackage{lineno}
  - \linenumbers
  - \usepackage[utf8]{inputenc}
  #- \DeclareUnicodeCharacter{0301}{*******} #Used for finding Unicode Errors in PDF
---

@@

${^\dagger}$ To whom correspondance should be adressed

>>>>

---
output:
  #bookdown::pdf_document2: 
    #toc: no
    #keep_tex: yes
  bookdown::word_document2: default
fig_caption: yes
always_allow_html: yes
bibliography: 
  references.bib
#csl: biomed-central.csl #get Zotero running to work
# These are LaTex settings to take care of floating figures/tables, line spacing, etc
header-includes:
  - \usepackage{endfloat}    
  - \usepackage{setspace}\doublespacing
  - \usepackage{lineno}
  - \linenumbers
  - \usepackage[utf8]{inputenc}
  #- \DeclareUnicodeCharacter{0301}{*******} #Used for finding Unicode Errors in PDF
---

@@

${^\dagger}$ To whom correspondence should be adressed
